---
title: 'Data Visualization with *ggplot2 extensions*'
author: 'Luca Valnegri'
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: 
    rmdformats::readthedown:
        theme: lumen
        highlight: tango
        code_fold: hide
        css: 'https://datamaps.uk/assets/WeR/nb.css'
---

# Setting up 

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
geo_path <- 'https://datamaps.uk/geography/'
data_path <- 'https://datamaps.uk/datasets/'
bnd_path <- 'https://datamaps.uk/boundaries/uk/rds/'
```

Load the *ggplot2* package. Install it if it's not found.
```{r}
if(!require(ggplot2)) install.packages('ggplot2')
library(ggplot2)
```

Load some *ggplot2* extensions. Install any that are not found.
```{r}
pkgs <- list('ggiraph', 'ggrepel', 'ggridges')
lapply(pkgs, function(x){
    if(!require(x)) install.packages(x)
    library(x)
})
```

Load the dataset *diamond* from the [ggplot2](https://ggplot2.tidyverse.org/) package: 
```{r}
data(diamonds, package = c('ggplot2'))
str(diamonds)
diamonds
```
The *diamonds* dataset contains information about 10 attributes of nearly 54,000 diamonds


Load the *Human Development Index (HDI)* dataset from the [UN Development Programme Website](http://hdr.undp.org/en/data) using the [readr](https://readr.tidyverse.org/) package: 
```{r}
if(!require(readr)) install.packages('readr')
hdi <- readr::read_csv('./data/hdi.csv', skip = 1, na = c('', '..'))
str(hdi)
hdi
```


Load the *Online Retail* dataset from the [UC Irvine Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/online+retail) using the [readxl](https://readxl.tidyverse.org/) package: 
```{r}
if(!require(readxl)) install.packages('readxl')
retail <- readxl::read_xlsx('./data/retail.xlsx')
str(retail)
retail
```




# Datasets

  - Package Internals:
    - *iris* and *mtcars* from `base`
    - *msleep* from `ggplot2`
    - *diamonds* from `ggplot2`
    - *gapminder* from `gapminder`
    - *flights* from `nycflights13`
    - *storms* from `dplyr`

  - [Ames Housing Dataset](https://ww2.amstat.org/publications/jse/v19n3/decock.pdf)

  - [UCI Online Retail](https://archive.ics.uci.edu/ml/datasets/online+retail)

  - [Human Development Index](http://hdr.undp.org/en/data) by Country
  
  - [Corruption Perceptions Index](https://www.transparency.org/research/cpi) by Country
  
  - [UK House Price Index](https://www.ons.gov.uk/economy/inflationandpriceindices/bulletins/housepriceindex/previousReleases) 
  
  - [UK Gender Paygap](https://gender-pay-gap.service.gov.uk/) by Business Company
    
  - [UK Petitions](https://petition.parliament.uk/petitions/) by Constituency
  
  - [UK Elections Results](https://researchbriefings.parliament.uk/ResearchBriefing/Summary/CBP-8647) by Constituency

  - [Brexit Referendum Results](https://www.electoralcommission.org.uk/who-we-are-and-what-we-do/elections-and-referendums/past-elections-and-referendums/eu-referendum/results-and-turnout-eu-referendum) by Local Authority

  - [UK Electoral Statistics](https://www.ons.gov.uk/peoplepopulationandcommunity/elections/electoralregistration/datasets/electoralstatisticsforuk) by Constituency

  - [UK Population Mid-Year Estimates](https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/parliamentaryconstituencymidyearpopulationestimates) by Constituency

  - [UK Food shops Ratings](https://ratings.food.gov.uk/) by Local Authority and Shop
  
  - [Airbnb Listings](http://insideairbnb.com/get-the-data.html) by City
  
  - [UK Crime Accident](https://data.police.uk/data/) by Lower Layer Super Output Area

  - [London Cycling Scheme](https://cycling.data.tfl.gov.uk/) by Single Trip for every Bike Station

  - [UK Flights Punctuality](https://www.caa.co.uk/Data-and-analysis/UK-aviation-market/Flight-reliability/Datasets/UK-flight-punctuality-data/) by Airport

  - [Geography Locations and Lookups](https://geoportal.statistics.gov.uk/)
